Modelling last glacial cycle ice dynamics in the Alps

### 2017-07-04 articles/cycle/alps-cycle.tex
Rework outline into standard (not Nature) format.
Giving up on Nature and the like. I prefer to promote a somewhat ethical
open-access publisher instead.

% ----------------------------------------------------------------------
\section{Main}
% ----------------------------------------------------------------------

\subsection{Introduction}

@@

\subsection{Glacier dynamics}
    Fig.~\ref{fig:lgmvel} -- Snapshot at 21\,ka and volume time series.\\
    Fig.~\ref{fig:timing} -- Timing of the LGM and area time series.\\
    Fig.~\ref{fig:profiles} -- Individual glacier extent profiles.

@@

\subsection{Erosion potential}
    Fig.~\ref{fig:erosion} -- Integrated erosion potential.

@@

% ----------------------------------------------------------------------
\section{Methods}
% ----------------------------------------------------------------------

\subsection{Ice sheet model set-up}
    Table~\ref{tab:params} -- Model parameters\\
    Fig.~\ref{fig:inputs} -- Climate and geothermal model inputs.\\

\subsection{Palaeo-climate forcing}
    Table~\ref{tab:records} -- Palaeo-climate records.\\
    Fig.~\ref{fig:timeseries} -- Low-resolution time series.\\
    Fig.~\ref{fig:footprints} -- Low-resolution ice cover.

@@

% ----------------------------------------------------------------------
% Supplementary tables
\clearpage
\setcounter{table}{0}
\renewcommand{\thetable}{S\arabic{table}}%
% ----------------------------------------------------------------------

@@

        $D$     & Lithosphere flexural rigidity
                & $5\e{24}$
                & \unit{N}
                & \citet{Lingle.Clark.1985} \\

@@

% ----------------------------------------------------------------------
% Supplementary figures
\clearpage
\setcounter{figure}{0}
\renewcommand{\thefigure}{S\arabic{figure}}%
% ----------------------------------------------------------------------

>>>>

% ----------------------------------------------------------------------
\section{Introduction}
% ----------------------------------------------------------------------

@@

% ----------------------------------------------------------------------
\section{Ice sheet model set-up}
% ----------------------------------------------------------------------

    Table~\ref{tab:params} -- Model parameters\\
    Fig.~\ref{fig:inputs} -- Climate and geothermal model inputs.\\

% ----------------------------------------------------------------------
\section{Palaeo-climate forcing}
% ----------------------------------------------------------------------

    Table~\ref{tab:records} -- Palaeo-climate records.\\
    Fig.~\ref{fig:timeseries} -- Low-resolution time series.\\
    Fig.~\ref{fig:footprints} -- Low-resolution ice cover.

% ----------------------------------------------------------------------
\section{Glacier dynamics}
% ----------------------------------------------------------------------

    Fig.~\ref{fig:lgmvel} -- Snapshot at 21\,ka and volume time series.\\
    Fig.~\ref{fig:timing} -- Timing of the LGM and area time series.\\
    Fig.~\ref{fig:profiles} -- Individual glacier extent profiles.

@@

% ----------------------------------------------------------------------
\section{Erosion potential}
% ----------------------------------------------------------------------

    Fig.~\ref{fig:erosion} -- Integrated erosion potential.

@@

% ----------------------------------------------------------------------
\section{Conclusions}
% ----------------------------------------------------------------------

    \begin{itemize}
    \item Summary of the previous stuff.
    \end{itemize}

@@

% ----------------------------------------------------------------------
% Tables
\clearpage
% ----------------------------------------------------------------------

@@

        $D$     & Lithosphere flexural rigidity
                & $5\e{24}$
                & \unit{N\,m}
                & \citet{Lingle.Clark.1985} \\

@@
